Collaborative Visual Analysis on the Web with RCloud

### 2015-06-16 discussion.tex
working

\paragraph*{Modularity and granularity} The ability to partition work into
independent units (modularity) is a key to working productively in teams.
It is good if the units can be kept small or granular, so team members can
realize benefits at least proportional to the work on the units.
RCloud's notebook and versioning capabilities allow work to be divided
into units as fine as the underlying language allows, and versioning
encourages making incremental changes at low cost and without disrupting
the work of others.

@@

\paragraph*{Content export} is not a capability we aimed at supporting,
and R already has many packages for this. Recently, due to popular
demand, we added user interface support for exporting plot images.
We assume that RCloud notebooks should play well in the ecosystem
of other tools, but sometimes it is difficult to know whether adding
a compatibility feature will offload complexity or bring more in.

@@

In existing R tools, the command prompt is used to try things out. It is very
fast and there is no commitment: nothing gets saved and there is nothing to
later clean up. In contrast, in RCloud's notebook interface, the extra cells need
to get deleted later, and there seems to be a mental burden that \emph{bad stuff
is getting saved}.

>>>>

\paragraph*{Modularity and granularity} Modularity, or the ability
to partition work into independent units is a key to working
productively in teams.
It is good if the units can be kept small or granular, so team members can
realize benefits at least proportional to the work on the units.
RCloud's notebook and versioning capabilities allow work to be divided
into units as fine as the underlying language allows, and versioning
encourages making incremental changes at low cost and without disrupting
the work of others.

@@

\paragraph*{Content export} is not a capability we aimed at supporting,
and R already has many packages for this. Recently, due to popular
demand, we added user interface support for exporting plot images.
We assume that RCloud notebooks should play well in the ecosystem
of other tools, but sometimes it is difficult to know whether adding
a feature for compatibility will offload complexity, or increase it.

@@

In existing R tools, the command prompt is used to try things out. It is very
fast and there is no commitment: nothing gets saved and there is nothing to
clean up. In contrast, in RCloud's notebook interface, the extra cells need
to be deleted later, and there seems to be a mental burden that \emph{bad stuff
is getting saved}.

### 2015-06-16 introduction.tex
working

\item Technology transfer.
In most organizations, development of analyses and visualizations 
s done by \emph{hackers} and \emph{scripters} (adopting Kandel et al.'s
terminology~\cite{Kandel:2012:EDA}). \emph{Application users} 
gain the benefits of the tools developed by hackers and scripters.
Results of experiments are often shared first by copying screen
shots or static output.  By the time decisions are made based on
the results of that screenshot, data and processes may have changed
so much that the decision can be wrong.
\stephen{Transitional sentence here.}
Generally, the connection between these two worlds is made by IT staff,
who port or rewrite code so it can run as a stable production service.
In an environment where business needs can change rapidly, this
process does not scale. Our goal is to merge the worlds of EDA and
production.

@@

\item Many tools adopt a standalone or single developer perspective,
not suited to collaboration and web deployment. 
\item Analysts find insufficient support for tracing events or issues from production back to the EDA process.
\end{itemize}

In view of the opportunity to improve this situation,
we created a software environment that supports the end-to-end
visual analytics process for individuals and teams and
their work within larger organizations.

>>>>

\item Technology transfer.
In most organizations, development of analyses and visualizations 
s done by \emph{hackers} and \emph{scripters} (adopting Kandel et al.'s
terminology~\cite{Kandel:2012:EDA}). \emph{Application users} 
gain the benefits of the tools developed by hackers and scripters.
Results of experiments are often shared first by copying screen
shots or static output.  By the time decisions are made based on
the results of that screenshot, data and processes may have changed
so much that the decision can be wrong.
\stephen{Transitional sentence here.}
Generally, the connection between these two worlds is made by IT staff,
who port or rewrite code so it can run as a stable production service.
In an environment where business needs can change rapidly, this
process does not scale. It is also difficult to trace problems
from production back to EDA.
Our goal is to merge the worlds of EDA and production to close this gap.

@@

In consideration of the opportunity to improve this situation,
we created a software environment that supports the end-to-end
visual analytics process for individuals and teams and
their work within larger organizations.
